A holomorphic approach to membranes and fivebranes

### 2022-08-05 fivebranes/kr.tex
merge

In \cite{KR2}, a $\Z$-graded decomposition of $E(5|10)$ is defined which has the property that the weight zero subalgebra is isomorphic to the exceptional super Lie algebra $E(3|6)$.
We compare our decomposition of the $!$-dual factorization algebra of $\clie^\bu(\cL_{sugra})$ on the complex three-fold $Z = \C^3$, see \S \ref{s:flatdecomp}, to this decomposition considered in \cite{KR2}.
Naturally, every other graded summand appearing in the decomposition of $E(5|10)$ is a module for $E(3|6)$---it turns out that every module that appears in this way is irreducible.
Following the description of these irreducible modules constructed in \cite{KR1,KR2} we compute (un)refined characters and proceed to give a conjectural procedure for computing (un)refined fivebrane indices.

There is a different decomposition of $E(5|10)$ (and its central extension) which has as its weight zero piece the subalgebra $E(1|6)$; this decomposition is natural from the point of view of membranes.
We comment on this in \S \ref{sec:membraneindex}.
%an embedding of $E(3|6)$ into $E(5|10)$ is constructed by considering the following auxiliary weight grading on the super Lie algebra $E(5|10)$. 
%We first split the coordinates on the formal five-disk as
%\[
%(z_i ; w_a) \in \Hat{D}^3 \times \Hat{D}^2 .
%\]
%In the fivebrane picture, the coordinates $z_i$ parameterize the holomorphic directions along the brane and the coordinates $w_a$ are the holomorphic coordinates transverse to the brane.

@@

We begin by turning to the algebraic side of things and start by recalling the weight decomposition of $E(5|10)$ constructed in \cite{KR2}.
In \S \ref{s:m5localops} we return to fivebranes and use this to give a  characterization of local operators of the twisted theory.

@@

The twist of eleven-dimensional supergravity is more closely related to an $L_\infty$ central extension of $E(5|10)$ of the form
\[
0 \to \C \to \Hat{E(5|10)} \to E(5|10) \to 0 .
\]
See \cite[\S 3]{RSW}. 
The central extension is defined by the (totally even) three-linear cocycle
\beqn\label{eqn:e510central}
(\mu, \mu' , \alpha) \mapsto \<\mu \wedge \mu' , \alpha\>_{z=w=0} \in \C .
\eeqn
Since this is a three-linear functional the model we use for the central extension is a super $L_\infty$ algebra (with zero one-ary operation) rather than just a super Lie algebra.

@@

There is another auxiliary grading that we will make use of which is also defined in \cite{KR,KacClass}. 
The super Lie algebra $E(5|10)$ carries a (non-cohomological) consistent $\Z$-grading by declaring 
\begin{itemize}
\item $\deg z_i = \deg w_a = 2$, so that $\deg \del_{z_i} = \deg \del_{w_a} = -2$. 
\item Parity carries an additional degree of $-3/2$, so that $\deg \d z_i = \deg \d w_a = -1/2$.
\end{itemize}
This consistent $\Z$-grading extends to the central extension of $E(5|10)$ by declaring that the central term has degree $-5$. 
To distinguish this from the `weight' grading above, we will refer to this grading as `degree'.

@@

For $\lambda_1 \geq 0$ define the polynomial in the variables $t_i^{\pm 1}$ and an auxiliary variable $x$
\beqn\label{eqn:p}
p_{\lambda_1}(t_1,t_2,x) = t_1^{\lambda_1} t_2^{-\lambda_1} \left(1 + (1+t_1^{-1} t_2^{-1} - t_1^{-1} x) h(t_1,t_2,x)\right) 
\eeqn
where for $\lambda_1 > 0$
\beqn\label{eqn:h1}
h_{\lambda_1}(t_1,t_2,x) = t_2 (t_1^{-1} t_2 - x) \left(1 + t_1^{-1} t_2^2 + \cdots + t_1^{-\lambda_1+1} t_2^{2 \lambda_2 -2}\right)  
\eeqn
and for $\lambda_1 = 0$ we set $h_0 (t_1,t_2,x) = 0$.

Our main result of this section is the following.
\begin{thm}
\label{thm:refinedA}
For any $\lambda_1,\lambda_3 \geq 0$ the character of $\til I_A(\lambda_1,\lambda_3)$ is given by the following expression
\begin{multline}
\frac{t^{2 \lambda_1 - 3 \lambda_3+6}}{(1-t_1^{-1} t^2)(1-t_1t_2^{-1}t^2)(1-t_2 t^2)(1-r^{-2})} \times \\
\left(r^{\lambda_3} p_{\lambda_1}(t_1,t_2,t^{-1} r) (1-t_1^{-1} r^{-1} t^{-1})(1-t_1t_2^{-1} r^{-1} t^{-1})(1-t_2 r^{-1} t^{-1}) \right.
\\
- \left. r^{-\lambda_3 - 2} p_{\lambda_1}(t_1,t_2,r^{-1} t^{-1})(1-t_1^{-1} r t^{-1})(1-t_1t_2^{-1} r t^{-1})(1-t_2 r t^{-1}) \right)
\end{multline}
\end{thm}

@@

\begin{lem}
\label{lem:generating}
One has
\beqn
\til p_{\lambda_1} (t_1,t_2,x) = \frac{p_{\lambda_1}(t_1,t_2,x)}{(1-t_1^{-1} x)(1-t_1t_2^{-1} x)(1-t_2 x)} .
\eeqn
where the polynomial $p_{\lambda_1}(x,t_1,t_2)$ is given by equation \eqref{eqn:p}.

\end{lem} 
\begin{proof}
We start by expanding the expression for the generating function $\til p_{\lambda_1}(t_1,t_2,x)$:
\begin{multline}
t_1^{\lambda_1} t_2^{-\lambda_1} \sum_{j \geq 0} t_1^{j} t_2^{-j} x^j \sum_{k=0}^{\lambda_1 + j}t_1^{-k} t_2^{2k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j \geq 0} \sum_{k=0}^{\lambda_1 + j} t_1^{j-k} t_2^{-j+2k} x^j \left(1 - t_1^{-k-1} t_2^{-k-1}\right) \\ 
= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j \geq 0} \left(t_1^j t_2^{-j} \frac{1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1}}{1-t_1^{-1} t_2^{2}} - t_1^{j-1} t_2^{-j-1} \frac{1 - (t_1^{-2} t_2)^{\lambda_1+j+1}}{1 - t_1^{-2} t_2} \right) x^j  \\
%= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{(1-t_1^{-1} t_2^{2})} \sum_{j \geq 0} \left( t_1^j t_2^{-j} (1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1})(1 - t_1^{-2} t_2) \right. \\ \left. - t_1^{j-1} t_2^{-j-1} (1 - (t_1^{-2} t_2)^{\lambda_1+j+1})(1-t_1^{-1} t_2^{2}) \right) x^j \\ 
= F(t_1,t_2) \left( G_1 (t_1,t_2,x) - t_1^{-1} t_2^{-1} G_2 (t_1,t_2,x)\right) .
\end{multline}

@@

Now, the proof of Theorem \ref{thm:refinedA} is an immediate computation. 
\begin{multline}
\ch \til I_A(\lambda_1,\lambda_2) = \frac{t^{2 \lambda_1 - 3 \lambda_3} R}{1-r^{-2}} \left(r^{\lambda_3} \frac{p_{\lambda_1}(t_1,t_2,r t^{-1})}{(1-t_1^{-1} r t^{-1})(1-t_1t_2^{-1} r t^{-1})(1-t_2 r t^{-1})}  \right. \\ \left. - r^{-\lambda_3-2} \frac{p_{\lambda_1}(t_1,t_2,r^{-1} t^{-1})}{(1-t_1^{-1} r^{-1} t^{-1})(1-t_1t_2^{-1} r^{-1} t^{-1})(1-t_2 r^{-1} t^{-1})}\right) \\  
= \frac{t^{2 \lambda_1 - 3 \lambda_3+6}}{(1-t_1^{-1} t^2)(1-t_1t_2^{-1}t^2)(1-t_2 t^2)(1-r^{-2})} \times \\
\left(r^{\lambda_3} p_{\lambda_1}(t_1,t_2,t^{-1} r) (1-t_1^{-1} r^{-1} t^{-1})(1-t_1t_2^{-1} r^{-1} t^{-1})(1-t_2 r^{-1} t^{-1}) \right.
\\
- \left. r^{-\lambda_3 - 2} p_{\lambda_1}(t_1,t_2,r^{-1} t^{-1})(1-t_1^{-1} r t^{-1})(1-t_1t_2^{-1} r t^{-1})(1-t_2 r t^{-1}) \right) .
\end{multline}

@@

Note that upon substituting $q = t^2$ this agrees with the our direct computation of the character of local operators on the holomorphic twist of the six-dimensional theory abelian superconformal theory from Proposition \ref{prop:6done}.

@@

Again, we note that upon substituting $q = t^2$ this agrees with the our direct computation of the character of local operators on the holomorphic twist of our conjectural description of the six-dimensional superconformal theory associated to the Lie algebra $\lie{sl}(2)$ which we computed in Proposition \ref{prop:6dtwo}.

@@

\begin{thm}
\label{thm:chB}
For $\lambda_3 \geq 0$ the character $\ch \til I_B(0,\lambda_3)$ is given by the expression
\begin{multline}
\label{eqn:chB3}
\frac{t^{2 \lambda_3 + 6} R(t,t_1,t_2,r)}{1-r^{-2}} \left(r^{\lambda_3} \til q_{\lambda_3} (t_1,t_2,t^{-1}r^{-1}) - r^{-\lambda_3-2} \til q_{\lambda_3} (t_1,t_2,t^{-1}r) \right) \\ + \frac{t^{2 \lambda_3+10}}{(1-t_1^{-1} t^2)(1-t_1t_2^{-1}t^2)(1-t_2 t^2)(1-r^{-2})} \times \\
\left(p_{\lambda_3+2}(t_1,t_2,t^{-1} r) (1-t_1^{-1} r^{-1} t^{-1})(1-t_1t_2^{-1} r^{-1} t^{-1})(1-t_2 r^{-1} t^{-1}) \right.
\\
- \left. r^{-2} p_{\lambda_3+2}(t_1,t_2,r^{-1} t^{-1})(1-t_1^{-1} r t^{-1})(1-t_1t_2^{-1} r t^{-1})(1-t_2 r t^{-1}) \right)
\end{multline}
where the polynomial $p_{\lambda_3 + 2}(x)$ is as in Theorem \ref{thm:refinedA}.
\end{thm}

\begin{proof}
We have already computed $\ch\til I_A(\lambda_1,\lambda_3)$ for any pair $(\lambda_1,\lambda_3)$ in Theorem~\ref{thm:refinedA}.
The formula for $\ch \til I_A(\lambda_3+2,0)$ accounts for the last two lines in the stated formula.

It suffices to compute the character of the modified type $B$ Verma modules 
\[
\til M_{B}(k,\lambda_3-k) .
\]

@@

Notice that since $R(t=r) = 0$ it follows that if we further specialize at $t = r$ and substitute $q = t^2$ then the first line of \eqref{eqn:chB3} vanishes so that
\beqn
\ch \til I_B(0,\lambda_3)|_{t=r, t_i=1} = \ch \til I_A(\lambda_3+2,0)|_{t=r, t_i=1} = \frac{q^{\lambda_3 + 1}}{1 - q} .
\eeqn

\parsec[s:firstcase]

Let's unpack the character of the simplest module of type $B$, namely $\til I_B(0,0)$.

@@

\subsection{Decomposing fivebrane local operators}

>>>>

In \cite{KR2}, a $\Z$-graded decomposition of $E(5|10)$ is defined which has the property that the weight zero subalgebra is isomorphic to the exceptional super Lie algebra $E(3|6)$.
We compare our decomposition of the $!$-dual factorization algebra of $\clie^\bu(\cL_{sugra})$ on the complex three-fold $Z = \C^3$, see \S \ref{s:fact}, to this decomposition considered in \cite{KR2}.
Naturally, every other graded summand appearing in the decomposition of $E(5|10)$ is a module for $E(3|6)$---it turns out that every module that appears in this way is irreducible.
Following the description of these irreducible modules constructed in \cite{KR1,KR2} we compute (un)refined characters and proceed to give a conjectural procedure for computing (un)refined fivebrane indices.

There is a different decomposition of $E(5|10)$ (and its central extension) which has as its weight zero piece the subalgebra $E(1|6)$; this decomposition is natural from the point of view of membranes.
We comment on this in \S \ref{sec:kacmembrane}.
%an embedding of $E(3|6)$ into $E(5|10)$ is constructed by considering the following auxiliary weight grading on the super Lie algebra $E(5|10)$. 
%We first split the coordinates on the formal five-disk as
%\[
%(z_i ; w_a) \in \Hat{D}^3 \times \Hat{D}^2 .
%\]
%In the fivebrane picture, the coordinates $z_i$ parameterize the holomorphic directions along the brane and the coordinates $w_a$ are the holomorphic coordinates transverse to the brane.

@@

We begin by turning to the algebraic side of things and start by recalling the weight decomposition of $E(5|10)$ constructed in \cite{KR2}.
In \S \ref{s:kacfivebrane} we return to fivebranes and use this to give a  characterization of local operators of the twisted theory.

@@

The twist of eleven-dimensional supergravity is more closely related to an $L_\infty$ central extension of $E(5|10)$ of the form
\[
0 \to \C \to \Hat{E(5|10)} \to E(5|10) \to 0 .
\]
See \cite[\S 3]{RSW}, and \S \ref{s:kacfivebrane}.
The central extension is defined by the (totally even) three-linear cocycle
\beqn\label{eqn:e510central}
(\mu, \mu' , \alpha) \mapsto \<\mu \wedge \mu' , \alpha\>_{z=w=0} \in \C .
\eeqn
Since this is a three-linear functional the model we use for the central extension is a super $L_\infty$ algebra (with zero one-ary operation) rather than just a super Lie algebra.

@@

There is another auxiliary grading that we will make use of which is also defined in \cite{KR2,KacClass}. 
The super Lie algebra $E(5|10)$ carries a (non-cohomological) consistent $\Z$-grading by declaring 
\begin{itemize}
\item $\deg z_i = \deg w_a = 2$, so that $\deg \del_{z_i} = \deg \del_{w_a} = -2$. 
\item Parity carries an additional degree of $-3/2$, so that $\deg \d z_i = \deg \d w_a = -1/2$.
\end{itemize}
This consistent $\Z$-grading extends to the central extension of $E(5|10)$ by declaring that the central term has degree $-5$. 
To distinguish this from the `weight' grading above, we will refer to this grading as `degree'.

@@

For $\lambda_1 \geq 0$ define the polynomial in the variables $t_i^{\pm 1}$ and an auxiliary variable $x$
\beqn\label{eqn:p}
p_{\lambda_1}(t_1,t_2,x) = t_1^{\lambda_1} t_2^{-\lambda_1} \left(1 + (1+t_1^{-1} t_2^{-1} - t_1^{-1} x) h_{\lambda_1}(t_1,t_2,x)\right) 
\eeqn
where for $\lambda_1 > 0$
\beqn\label{eqn:h1}
h_{\lambda_1}(t_1,t_2,x) = t_2 (t_1^{-1} t_2 - x) \left(1 + t_1^{-1} t_2^2 + \cdots + t_1^{-\lambda_1+1} t_2^{2 \lambda_1 -2}\right)  
\eeqn
where the sum in parentheses has $\lambda_1$ terms.
For $\lambda_1 = 0$ we set $h_0 (t_1,t_2,x) = 0$.

Our main result of this section is the following.
\begin{thm}
\label{thm:refinedA}
For any $\lambda_1,\lambda_3 \geq 0$ the character of $\ch \til I_A(\lambda_1,\lambda_3)$ is given by the following expression
\begin{multline}
\frac{t^{2 \lambda_1 - 3 \lambda_3+6}}{(1-t_1^{-1} t^2)(1-t_1t_2^{-1}t^2)(1-t_2 t^2)(1-r^{-2})} \times \\
\left(r^{\lambda_3} p_{\lambda_1}(t_1,t_2,t^{-1} r) (1-t_1^{-1} r^{-1} t^{-1})(1-t_1t_2^{-1} r^{-1} t^{-1})(1-t_2 r^{-1} t^{-1}) \right.
\\
- \left. r^{-\lambda_3 - 2} p_{\lambda_1}(t_1,t_2,r^{-1} t^{-1})(1-t_1^{-1} r t^{-1})(1-t_1t_2^{-1} r t^{-1})(1-t_2 r t^{-1}) \right)
\end{multline}
where $p_{\lambda_1}$ is as in equation \eqref{eqn:p}.
\end{thm}

@@

\begin{lem}
\label{lem:generating}
One has
\beqn
\til p_{\lambda_1} (t_1,t_2,x) = \frac{p_{\lambda_1}(t_1,t_2,x)}{(1-t_1^{-1} x)(1-t_1t_2^{-1} x)(1-t_2 x)} .
\eeqn
where the polynomial $p_{\lambda_1}(t_1,t_2,x)$ is given by equation \eqref{eqn:p}.

\end{lem} 
\begin{proof}
We start by expanding the expression for the generating function $\til p_{\lambda_1}(t_1,t_2,x)$:
\begin{multline}
\label{eqn:long}
t_1^{\lambda_1} t_2^{-\lambda_1} \sum_{j \geq 0} t_1^{j} t_2^{-j} x^j \sum_{k=0}^{\lambda_1 + j}t_1^{-k} t_2^{2k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j \geq 0} \sum_{k=0}^{\lambda_1 + j} t_1^{j-k} t_2^{-j+2k} x^j \left(1 - t_1^{-k-1} t_2^{-k-1}\right) \\ 
= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j \geq 0} \left(t_1^j t_2^{-j} \frac{1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1}}{1-t_1^{-1} t_2^{2}} - t_1^{j-1} t_2^{-j-1} \frac{1 - (t_1^{-2} t_2)^{\lambda_1+j+1}}{1 - t_1^{-2} t_2} \right) x^j  \\
%= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{(1-t_1^{-1} t_2^{2})} \sum_{j \geq 0} \left( t_1^j t_2^{-j} (1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1})(1 - t_1^{-2} t_2) \right. \\ \left. - t_1^{j-1} t_2^{-j-1} (1 - (t_1^{-2} t_2)^{\lambda_1+j+1})(1-t_1^{-1} t_2^{2}) \right) x^j \\ 
= F(t_1,t_2) \left( G_1 (t_1,t_2,x) - t_1^{-1} t_2^{-1} G_2 (t_1,t_2,x)\right) .
\end{multline}

@@

Now, we plug these expressions into \eqref{eqn:long} and simplify to obtain
\begin{multline}
\ch \til I_A(\lambda_1,\lambda_2) = \frac{t^{2 \lambda_1 - 3 \lambda_3} R}{1-r^{-2}} \left(r^{\lambda_3} \frac{p_{\lambda_1}(t_1,t_2,r t^{-1})}{(1-t_1^{-1} r t^{-1})(1-t_1t_2^{-1} r t^{-1})(1-t_2 r t^{-1})}  \right. \\ \left. - r^{-\lambda_3-2} \frac{p_{\lambda_1}(t_1,t_2,r^{-1} t^{-1})}{(1-t_1^{-1} r^{-1} t^{-1})(1-t_1t_2^{-1} r^{-1} t^{-1})(1-t_2 r^{-1} t^{-1})}\right) \\  
= \frac{t^{2 \lambda_1 - 3 \lambda_3+6}}{(1-t_1^{-1} t^2)(1-t_1t_2^{-1}t^2)(1-t_2 t^2)(1-r^{-2})} \times \\
\left(r^{\lambda_3} p_{\lambda_1}(t_1,t_2,t^{-1} r) (1-t_1^{-1} r^{-1} t^{-1})(1-t_1t_2^{-1} r^{-1} t^{-1})(1-t_2 r^{-1} t^{-1}) \right.
\\
- \left. r^{-\lambda_3 - 2} p_{\lambda_1}(t_1,t_2,r^{-1} t^{-1})(1-t_1^{-1} r t^{-1})(1-t_1t_2^{-1} r t^{-1})(1-t_2 r t^{-1}) \right) .
\end{multline} 
This completes the proof of Theorem \ref{thm:refinedA}.

@@

We note that upon substituting $q = t^2$ this agrees with $\chi_{\lie{u}(1)}^{6d}(t_1,t_2,q,r)$---the character of local operators on the holomorphic twist of the abelian six-dimensional superconformal theory, see Proposition \ref{prop:6done}.

@@

Again, we note that upon substituting $q = t^2$ this agrees with $\chi_{\lie{sl}(2)}^{6d}(t_1,t_2,q,r)$---the character of local operators on the holomorphic twist of our conjectural description of the six-dimensional superconformal theory associated to the Lie algebra $\lie{sl}(2)$, see Proposition \ref{prop:6dtwo}.

We will see how these agreements for small values of $\lambda_1,\lambda_3$ fit into a more general relationship between the irreducible modules $\til I_A(\lambda_1,\lambda_3)$ and $\til I_{B} (\lambda_1,\lambda_3)$ and local operators of the universal fivebrane theory in \S \ref{s:kacfivebrane}.

@@

\begin{thm}
\label{thm:chB}
For $\lambda_3 \geq 0$ the character $\ch \til I_B(0,\lambda_3)$ is given by the expression
\begin{multline}
\label{eqn:chB3}
\frac{t^{2 \lambda_3 + 6} R(t,t_1,t_2,r)}{1-r^{-2}} \left(r^{\lambda_3} \til q_{\lambda_3} (t_1,t_2,t^{-1}r^{-1}) - r^{-\lambda_3-2} \til q_{\lambda_3} (t_1,t_2,t^{-1}r) \right) \\ + \frac{t^{2 \lambda_3+10}}{(1-t_1^{-1} t^2)(1-t_1t_2^{-1}t^2)(1-t_2 t^2)(1-r^{-2})} \times \\
\left(p_{\lambda_3+2}(t_1,t_2,t^{-1} r) (1-t_1^{-1} r^{-1} t^{-1})(1-t_1t_2^{-1} r^{-1} t^{-1})(1-t_2 r^{-1} t^{-1}) \right.
\\
- \left. r^{-2} p_{\lambda_3+2}(t_1,t_2,r^{-1} t^{-1})(1-t_1^{-1} r t^{-1})(1-t_1t_2^{-1} r t^{-1})(1-t_2 r t^{-1}) \right)
\end{multline}
where the polynomial $p_{\lambda_3 + 2}(x)$ is as in Theorem \ref{thm:refinedB}.
\end{thm}

\begin{proof}
We have already computed $\ch\til I_A(\lambda_1,\lambda_3)$ for any pair $(\lambda_1,\lambda_3)$ in Theorem~\ref{thm:refinedA}.
The formula for $\ch \til I_A(\lambda_3+2,0)$ accounts for the last three lines equation \eqref{eqn:chB3}.

It suffices to compute the character of the modified type $B$ Verma modules 
\[
\til M_{B}(l,\lambda_3-l) ,
\]
and to sum from $l = 0$ to $l = \lambda_3$. 
This is precisely the first line of \eqref{eqn:chB3}.

@@

Notice that since $R(t=r) = 0$ and that $\ch \til M_B$ is regular along $t=r$ it follows that if we specialize at $t = r$ and substitute $q = t^2$ then the first line of \eqref{eqn:chB3} vanishes so that
\beqn
\ch \til I_B(0,\lambda_3)|_{t=r, t_i=1} = \ch \til I_A(\lambda_3+2,0)|_{t=r, t_i=1} = \frac{q^{\lambda_3 + 1}}{1 - q} .
\eeqn

\parsec[s:Bfirstcase]

Let's unpack the character of the simplest module of type $B$, namely $\til I_B(0,0)$, that is $\lambda_3 = 0$ in equation \ref{eqn:chB2}.
Notice that $\til q_0 (t_1,t_2,x) = 1$, thus
\beqn
\ch \til M_B(0,0) = t^6 R(t_1,t_2,t,r) .
\eeqn

Next we need to compute \ch \til I_A(2, 0)$.
For this we refer to Theorem \ref{thm:refinedA}.
Notice that 
\[
p_

@@

\subsection{Decomposing fivebrane local operators}
\label{s:kacfivebrane}
